---
title: Untitled
format:
  modern2-cv-pdf: default
author: Samanwoy Mukhopadhyay
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvcolor: 
  main: B83B5E
  accent: 6A2C70
jobtitle: Bioinformatics Scientist
sidebar:
  image: 
  bullets:
    # - Kolkata, India
    # - Indian
  sections: 
    - name: Contact
      items:
        - icon: map-marker
          text: Bengaluru, India
        - icon: phone
          text: "+91 8981163530"
        - icon: envelope
          text: m.samanwoy@gmail.com
        - icon: home
          text: my website
          href: https://samanwoy1989.github.io/
        - icon: github
          text: my github
          href: https://github.com/samanwoy1989
    - name: Skills
      items:
        - text: Omics Data Analysis
          exp: 
            text: "10+ years"
            num: 1
        - text: R, RStudio, Linux
          exp: 
            text: "10+ yrs."
            num: 1
        - text: Python, Bash, SQL, Git, JIRA, Confluence
          exp: 
            text: "4+ yrs."
            num: 0.4
        - text: Rmarkdown,Jupyter, Quarto, Shiny
          exp: 
            text: "5+ yrs."
            num: 0.5
    # - name: Tools
    #   items:
    #     - Git
    #     - Jupyter
    #     - RStudio
    #     - VS Code
    #     - Terminal
    #     - JIRA, Confluence
    - name: Education
      items:
        - text: "Ph.D. in Biotechnology"
          inst: "University of Calcutta"
          time: "2021"
          details: "Thesis: Host Transcriptome Response in Septic Shock"
        # - text: "M.Sc. in Zoology"
        #   inst: "University of Calcutta"
        #   time: "2012"
execute: 
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, descr) {

    command_start <- "\\cvevent"
    tbl[[where]] <- gsub("\n", " \\\\newline ", tbl[[where]])
    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}",
        "{", tbl[[descr]], "}"
        )

    cat(res, sep = "\n\n\n")
}

cvproj <- function(tbl,what,role,items){
    command_start <- "\\cvproj"
    res <- paste0(
        command_start, "{", tbl[[what]], "}",
        "{", tbl[[role]], "}",
        "{", sapply(tbl[[items]], function(x)paste0(x,collapse = ", ")), "}"
    )

    cat(res, sep = "\n\n\n")
}
```

# Summary

I am a results-driven Bioinformatics Scientist with expertise in data analysis, quality assessment, and visualization, enabling me to provide critical insights that drive research and development. My experience includes direct client management from project planning through execution, identifying upsell opportunities. I excel in transforming complex datasets into actionable insights, driving advancements in biomedical sciences and supporting targeted therapy development. Please refer to [my website](https://samanwoy1989.github.io/) for my detailed [CV](https://samanwoy1989.github.io/CV.html) and [Publications](https://samanwoy1989.github.io/Publications.html).

# Experience

```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details,
    "Bioinformatics Scientist", "Elucidata", "2021 - Present", "I managed multiple client projects during my 3+ years in Industry. I worked as a technical subject matter expert for a number of projects that helped my clients achieve high quality insights that saved them time and cost getting meaning ful results to achieve there goal faster. this was mostly pharma companies trying to find drug targets or responsible for various diseases.",
    "Senior Research Fellow(PhD)", "National Institute of Biomedical Genomics", "2016 - 2020",
    "I conducted research on a diverse range of bacterial infections, with a primary focus on host responses in sepsis, viral cancers, and COVID-19. I utilized various transcriptomic technologies to drive these investigations.",
    "Junior Research Fellow(PhD)", "National Institute of Biomedical Genomics", "2013 - 2015", "I conducted both wet lab and dry lab experiments, from collecting samples in hospitals to generating transcriptome data for my PhD project. My research focused on studying the host transcriptome response to bacterial sepsis."
) |>
    cvevents(when = "dates", what = "role", where = "institution", descr = "details")
```

# Projects

See my [github profile](https://github.com/samanwoy1989){style="color: red;"} for a comprehensive list of open source projects.\

```{r}
#| label: proj
#| output: asis
tibble::tribble(
    ~what, ~role, ~items,
    "Single-Cell RNASeq and Gene Similarity Analysis (2022-2024)", "Technical SME", c("Analyzed single-cell RNASeq data and established pipelines for gene similarity in siRNA treatments. Enhanced research capabilities, streamlined data analysis processes, and saved significant time and financial resources for clients by facilitating the development of targeted therapies."),
    "Cancer and Transcriptomics Projects (2021-2024)", "Technical SME", c("Conducted transcriptomics, proteomics, and meta-analysis across various cancers for different clients. Streamlined data analysis, accelerated insights into diverse cancer types, and delivered actionable results efficiently as a Technical SME."),
    "Role of a specific protein in COVID-19 through omics data analysis", "Technical SME",
    c("Evaluated the role of a protein of interest in COVID-19 through omics data analysis, providing critical insights. Accelerated research efforts, saved significant time and costs in planning future experiments for a reputed academic lab as a Technical SME.")
) |>
    cvproj(what = "what", role = "role", items = "items")

```
