---
title: Untitled
format:
  modern2-cv-pdf: default
author: Samanwoy Mukhopadhyay
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvcolor: 
  main: B83B5E
  accent: 6A2C70
jobtitle: Bioinformatics Scientist
sidebar:
  # image: 
  bullets:
    # - Kolkata, India
    # - Indian
  sections: 
    - name: Contact
      items:
        # - icon: map-marker
        #   text: Bengaluru, India
        - icon: phone
          text: "+91 8981163530"
        - icon: envelope
          text: m.samanwoy@gmail.com
        - icon: home
          text: my website
          href: https://samanwoy1989.github.io/
        - icon: github
          text: my github
          href: https://github.com/samanwoy1989
    - name: Skills
      items:
        - text: Omics Data Analysis
          exp: 
            text: "10+ years"
            num: 1
        - text: R, RStudio, Linux
          exp: 
            text: "10+ yrs."
            num: 1
        - text: Python, Bash, SQL, Git, JIRA, Confluence
          exp: 
            text: "4+ yrs."
            num: 0.4
        - text: Rmarkdown,Jupyter, Quarto, Shiny
          exp: 
            text: "5+ yrs."
            num: 0.5
    # - name: Tools
    #   items:
    #     - Git
    #     - Jupyter
    #     - RStudio
    #     - VS Code
    #     - Terminal
    #     - JIRA, Confluence
    - name: Education
      items:
        - text: "Ph.D. in Biotechnology"
          inst: "University of Calcutta"
          time: "2021"
          details: "Thesis: Host Transcriptome Response in Septic Shock"
        # - text: "M.Sc. in Zoology"
        #   inst: "University of Calcutta"
        #   time: "2012"
execute: 
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, descr) {

    command_start <- "\\cvevent"
    tbl[[where]] <- gsub("\n", " \\\\newline ", tbl[[where]])
    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}",
        "{", tbl[[descr]], "}"
        )

    cat(res, sep = "\n\n\n")
}

cvproj <- function(tbl,what,role,items){
    command_start <- "\\cvproj"
    res <- paste0(
        command_start, "{", tbl[[what]], "}",
        "{", tbl[[role]], "}",
        "{", sapply(tbl[[items]], function(x)paste0(x,collapse = ", ")), "}"
    )

    cat(res, sep = "\n\n\n")
}
```

# Summary

I am a results-driven Bioinformatics Scientist with expertise in data analysis, quality assessment, and visualization, enabling me to provide critical insights that drive research and development. My experience includes direct client management from project planning through execution, identifying up-sell opportunities. I excel in transforming complex datasets into actionable insights, driving advancements in biomedical sciences and supporting targeted therapy development. Please refer to [my website](https://samanwoy1989.github.io/) for my detailed [CV](https://samanwoy1989.github.io/CV.html) and [Publications](https://samanwoy1989.github.io/Publications.html).

# Experience

```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details,
    "Bioinformatics Scientist", "Elucidata", "2021 - Present", "Over the past 4 years in the industry, I have managed multiple client projects, primarily for pharmaceutical companies. As a technical subject matter expert in bioinformatics analysis, visualization, and insight generation, I have played a pivotal role in delivering high-quality insights. I handled projects ranging from oncology, analyzing tumor microenvironments and drug efficacy, to COVID-19 research, gene biomarker discovery, pathway enrichment, and survival analysis. Collaborating with various team members, I provided key insights that helped clients achieve their goals faster, significantly reducing time and costs. Additionally, I have interviewed and recruited individuals for various roles, fulfilling staffing needs multiple times.",
    "Senior Research Fellow(PhD)", "National Institute of Biomedical Genomics", "2016 - 2020",
    "As a senior research fellow, I led investigations into diverse bacterial infections, focusing on host responses in sepsis, viral cancers, and COVID-19 using advanced transcriptomic technologies. I mentored junior researchers, organized academic conferences, and promoted scientific collaboration, enhancing knowledge exchange and professional growth in the field.",
    "Junior Research Fellow(PhD)", "National Institute of Biomedical Genomics", "2013 - 2015", "As the first student under my supervisor, I gained hands-on experience in setting up a new lab, conducting a wide range of wet lab and dry lab experiments. My focus was on collecting clinical samples, generating transcriptome data for my PhD project, optimizing protocols, and managing grant writing and various documents for sample collection. These experiences significantly enhanced my expertise in clinical research methodologies."
) |>
    cvevents(when = "dates", what = "role", where = "institution", descr = "details")
```

# Projects

See my [website](https://samanwoy1989.github.io/){style="color: red;"} for a comprehensive list projects handled by me over the years. Mentioning a few Impactful Project here.

-   **Microbiome and Tuberculosis (2022-2024):** Conducted comprehensive audits and meta-analyses to ensure data reliability and accuracy, crucial for advancing Tuberculosis research for a leading organization.

-   **Cancer Biology (2022-2023):** Provided critical insights into tumor micro-environment and biology, evaluating the impact of treatments on tumor survival, pivotal for advancing cancer treatment strategies for multiple clients.

-   **Bioinformatics Packaged Solutions (2021-2024):** Developed and implemented custom bioinformatics analysis frameworks, offering tailored solutions for diverse scientific needs. These innovations were utilized as unique service offerings, enhancing client capabilities effectively.
